### 2012-12-04 inst/examples/policycosts/writeup.Rmd
finalized version of writeup.md

Fig4a <- ggplot(tmp2, aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  #geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.1) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4a
Fig4b <- ggplot(tmp2, aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  #geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.1) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4b
````

>>>>

Fig4a <- ggplot(tmp2, aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")

Fig4b <- ggplot(tmp2, aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4a
Fig4b
````
